Automatic Generation of Domain Models

### 2013-01-02 ontologies/paper.tex
fixed quotes and fixed captions for images

\author{David Przybilla\\dav.alejandro@gmail.com, davida@coli.uni-saarland.de\\ \\ Term Paper for Knowledge Representation Seminar\\ Universit\"{a}t des Saarlandes}
\title{Automatic Generation of Domain Models}
\begin{document}
\twocolumn[
	 \begin{@twocolumnfalse}
    \maketitle
  \end{@twocolumnfalse}
 ]

@@

Automatically creating knowledge representation from unstructured text has been a focus of study given the amount of data available in the web.
Projects such as 'Know it all'\footnote{\url{http://www.cs.washington.edu/research/knowitall/}} considers the problem of developing a variety of domain-independent systems that extract information from the Web in an autonomous, scalable way.\\ Google\footnote{\url{http://www.google.com/insidesearch/features/search/knowledge.html}} for example has the project 'The knowledge Graph' which considers the automatically construction of an ontology by using the web knowledge. \\
\\
Nevertheless the unstructured nature of the information has proven to be an challenge when constructing knowledge representations, natural languages arises many problems when trying to understand their semantics and to abstract concrete cases into general relations and entities.\\
In the opinion of this reviewer Information Extraction provided a first simple task into automatically creating structures from natural language texts. The task in information extraction consist in gathering  relations among entities from raw text.\\
In the first stages of this task only a very specific range of relations and entities are to be caught.
For example one would like to gather all relations and entities talking about  "getting the Nobel prize" or "change of chairs in a company".\\
However in the recent years this trend has evolved towards "Open Information Extraction", which wants to capture as much as entities and relations as possible given raw text.\\
The applications to information extraction are countless, the output of the task provide a resource for other more sophisticated processes, and it could be useful for example to topic mining, opinion mining or information retrieval or to correlate different relations or events captured from different sources.
In the opinion of the reviewer this provides a first step into building an ontology, since it would allow initially to have a candidate pool of concepts and relations.\\
\\
During the last years focus has been put into strategies which allow to capture structures in raw text, for example Cortez and Oliveira ~\cite{Cortez:2011:JUS:1989323.1989380} proposed a method for extracting data from semi-structured texts. In their experiments their system learns without human intervention the structures in which Cooking recipes are written and it is able to match each step and ingredients of the recipes into a structured representation.\\
This could be a major improvement since it would allow for example to capture entities and relations from soruces of knowledge that are semi-structured like Wikipedia.\\
\\
Additionally The reviewer would like to mention that even though there is a focus on creating Ontologies, there is also a focus on Extending the current ones in an automatic way.\\
Many tasks require Knowledge sources in order to achieve good performance, however this depends deeply on the coverage of the Knowledge representation. 
Consider for example the applications using Wordnet or Framenet, they heavily rely on the coverage of those sources to disambiguate the senses of the words.
In ~\cite{Tonelli:2013:WWM:2405838.2405917} Tonelli proposes a method for extending this Knowledge Sources by using Wikipedia in a semi-automatic way.
Following the same trend Yamada ~\cite{yamada-EtAl:2011:IJCNLP-2011} tries to extend Wordnet in an automatic way by using Wikipedia.\\
Following a different direction Pinkal,Regneri and Koller  in ~\cite{regneri-koller-pinkal:2010:ACL} propose the use of crowdsourcing to gather scripts of common activities (like shopping, cooking eggs) in order to model $Common\, Knowledge$ which is often overlooked by computer systems.

@@

	\item filling words (i.e : "um", "uhh")
\end{itemize}

@@

\begin{itemize}
	\item Stop Word Removal: Functional words which do not convey relevant meaning are removed (i.e: ''for",''of"..).

@@

\subsection{Clusterer}
The main idea of this step is to use a bisection clustering algorithm many times to have different clusters the documents.\\
The bisection algorithm receives as an input the number of clusters ($K$) and the documents. It progressively looks for clusters until the $K$ clusters are found.
\begin{figure*}[]
  \centering
    \includegraphics[scale=0.2]{pics/clusterer2.jpg}
    \caption{Clusterer}
   \label{fig:clusterer}  
\end{figure*}

@@

\begin{figure*}[]
  \centering
    \includegraphics[scale=0.2]{pics/taxonomyBuilder.jpg}
    \caption{Taxonomy Builder input and output}
   \label{fig:taxonomyBuilder}  
\end{figure*}

@@

\subsubsection*{Typical Actions}
The typical actions for each node are also gathered, that is the typical instructions that the agent should give the client.
The authors of the paper hypotheses that the actions are usually around the features of the product. So if they know that a feature is the "format button", then they know a verb around that noun will most likely  be an action.

@@

\subsubsection*{Questions and Answers}
Since their input is raw text, the authors mention that in order to capture the questions the use trigger words such as "how", "what","where" which should mark the beginning of a question.\\
Regarding to the answer, it would be the sentence following the question sentence.

@@

The overall construction of the taxonomy given the underlying idea of different granularities of topics seem to work. Nevertheless the reviewer wonders whether the expressiveness and coverage is enough for what it might be real applications that might actually benefit the agents or the users of the callcenter, for example if one were to extend the system into a Question answering System, then this representation will be surely not enough.\\
\\
In ~\cite{DBLP:conf/kdd/LiuSLW12} Liu proposes another method to create a taxonomy from keywords , however they handle different issues which were not addressed by the authors of the reviewed paper, for example fine grain domains and changing domains.\\
Liu proposes using Keywords and not text, since it would provide both an easy way for humans to read the taxonomy and ti will be easier to model how the taxonomy evolves and changes as the domain does.\\
Furthermore, Liu proposes a way to connect the keywords by using text clustering and Information Retrieval, and she addresses many issues not covered by the given paper, this issues are resolved by using information extraction.\\
One of the issues with BoW approach and hierarchical clustering is whether to trust or not the subtyping, for example the concept of 'vehicle insurance" and ''car insurance"  is clear that the later is a sub type of the earlier. Nevertheless from distributional perspective there is no way for the machine to assure to capture it this way, actually the reviewed paper mentions nothing about this, but it might be possible to have this subtype relations inverted given the distribution of the text. Liu on the other hand proposes to use information extraction snowball approach to look for patterns that might allow to capture some of the subtype,supertype relations, thus leaving this task not only to clustering step.\\
\\
A set of interesting remarks are made by  Bedini and Nguyen in ~\cite{artofontology} in their survey about automatic ontology generation they describe the life cycle of ontology generation. Namely they go in a general description of each phase as:
\begin{itemize}
	\item Extraction: The acquisition of Information and the processing of unstructured and semi-structured data
	\item Analysis: finding the relations and concepts int he given information, using heavily NLP techniques
	\item Generation: Translating the relations and concepts into the ontology formalism, as well as merging ontologies.
	\item Validation: A step to check possible wrong relations, usually as the authors mentioned made manually
	\item Evolution: The possibility of an incrementally growing ontology.
\end{itemize}
For the reviewer this life cycle gives an overview of what the authors of the reviewed paper has done, nevertheless the scalability of the proposed method does not leave space for incremental expansion of the taxonomy, that is in order to give evolution to the proposed methods the authors would have to re-run the whole system with the extra information.

@@

One could clearly see in Table~\ref{table:comparisonTable} that some systems admit some human interventions at some points, this could be beneficial since some steps regarding for example Word Sense Disambiguation could be very sensitive to the over all performance of the system.\\
\\
$Terminae$ ~\cite{BiebowSzulman:99} extracts keywords from the given corpora and hand it to an expert, whose task is to select the relevant terms and conceptualize them. Conceptualizing refers to first give a natural language definition of each term and then expressing it in terms of the chosen formalism to represent the ontology.\\
\\
$Salt$ ~\cite{Lonsdale02pepperingknowledge} on the other hand tries to go further by automatizing more parts of the process. Nevertheless it needs other knowledge sources in order to work. it assumes the existance of 3 types of knowledge: a general Knowledge representation of the domain, a dictionary to discover lexical relations among terms and a consistent set of texts. Salt also allows some interaction with the user, in the last stage for example introduces a new step called "Constraint Discovery" in which the user can state things such as "a person only has one birth date". \\
\\
The system proposed in Learning an OWL ontology from text ~\cite{citeulike:136652} is more recent than the previous mentioned ones. It heavily relies on Wordnet for connecting concepts. Nevertheless in the paper is mentioned how they extract the keywords that will be used later on in Wordnet, as a remark also nothing is mentioned about the verification process.\\
\\
It is also worth noticing how the reviewed paper does not describe much about the validation process.
Moreover both the extraction and Analysis part seems to be overlapping for the reviewed system, that could be because they proposed a rather simple structure ( Taxonomy of documents) as instead to a more complicated representation such relations among concepts.\\
A more complicated representation would definitely required a clear separation among those two phases, for example the analysis could required syntactic and Semantic processing to solve anaphoras, in order to be able to capture non-obvious relations given in the texts.

>>>>

\author{David Przybilla\\ \href{mailto:dav.alejandro@gmail.com}{dav.alejandro@gmail.com}, \href{mailto:davida@coli.uni-saarland.de}{davida@coli.uni-saarland.de}\\ \\ Term Paper for Knowledge Representation Seminar\\ Universit\"{a}t des Saarlandes}
\title{Automatic Generation of Domain Models}
\begin{document}
\twocolumn[
	 \begin{@twocolumnfalse}
    \maketitle
  \end{@twocolumnfalse}
 ]

@@

Automatically creating knowledge representation from unstructured text has been a focus of study given the amount of data available in the web.
Projects such as 'Know it all'\footnote{\url{http://www.cs.washington.edu/research/knowitall/}} considers the problem of developing a variety of domain-independent systems that extract information from the Web in an autonomous, scalable way.\\ Google\footnote{\url{http://www.google.com/insidesearch/features/search/knowledge.html}} for example has the project 'The knowledge Graph' which considers the automatically construction of an ontology by using the web knowledge. \\
\\
Nevertheless the unstructured nature of the information has proven to be an challenge when constructing knowledge representations, natural languages arises many problems when trying to understand their semantics and to abstract concrete cases into general relations and entities.\\
In the opinion of this reviewer Information Extraction provided a first simple task into automatically creating structures from natural language texts. The task in information extraction consist in gathering  relations among entities from raw text.\\
In the first stages of this task only a very specific range of relations and entities are to be caught.
For example one would like to gather all relations and entities talking about  ``getting the Nobel prize'' or ``change of chairs in a company''.\\
However in the recent years this trend has evolved towards ``Open Information Extraction'', which wants to capture as much as entities and relations as possible given raw text.\\
The applications to information extraction are countless, the output of the task provide a resource for other more sophisticated processes, and it could be useful for example to topic mining, opinion mining or information retrieval or to correlate different relations or events captured from different sources.
In the opinion of the reviewer this provides a first step into building an ontology, since it would allow initially to have a candidate pool of concepts and relations.\\
\\
During the last years focus has been put into strategies which allow to capture structures in raw text, for example Cortez and Oliveira ~\cite{Cortez:2011:JUS:1989323.1989380} proposed a method for extracting data from semi-structured texts. In their experiments their system learns without human intervention the structures in which Cooking recipes are written and it is able to match each step and ingredients of the recipes into a structured representation.\\
This could be a major improvement since it would allow for example to capture entities and relations from soruces of knowledge that are semi-structured like Wikipedia.\\
\\
Additionally The reviewer would like to mention that even though there is a focus on creating Ontologies, there is also a focus on Extending the current ones in an automatic way.\\
Many tasks require Knowledge sources in order to achieve good performance, however this depends deeply on the coverage of the Knowledge representation. 
Consider for example the applications using Wordnet or Framenet, they heavily rely on the coverage of those sources to disambiguate the senses of the words.
In ~\cite{Tonelli:2013:WWM:2405838.2405917} Tonelli proposes a method for extending this Knowledge Sources by using Wikipedia in a semi-automatic way.
Following the same trend Yamada ~\cite{yamada-EtAl:2011:IJCNLP-2011} tries to extend Wordnet in an automatic way by using Wikipedia.\\
Following a different direction Pinkal,Regneri and Koller  in ~\cite{regneri-koller-pinkal:2010:ACL} propose the use of crowdsourcing to gather scripts of common activities (like shopping, cooking eggs) in order to model $Common\, Knowledge$ which is often overlooked by computer systems.

@@

	\item filling words (i.e : ``um'', ``uhh'')
\end{itemize}

@@

\begin{itemize}
	\item Stop Word Removal: Functional words which do not convey relevant meaning are removed (i.e: ``for'',``of''..).

@@

\subsection{Clusterer}
The main idea of this step is to use a bisection clustering algorithm many times to have different clusters the documents.\\
The bisection algorithm receives as an input the number of clusters ($K$) and the documents. It progressively looks for clusters until the $K$ clusters are found.
\begin{figure*}[]
  \centering
    \includegraphics[scale=0.2]{pics/clusterer2.jpg}
    \caption{Clusterer - Clusters with different Granularity}
   \label{fig:clusterer}  
\end{figure*}

@@

\begin{figure*}[]
  \centering
    \includegraphics[scale=0.2]{pics/taxonomyBuilder.jpg}
    \caption{Input and Output of the Taxonomy Builder Component}
   \label{fig:taxonomyBuilder}  
\end{figure*}

@@

\subsubsection*{Typical Actions}
The typical actions for each node are also gathered, that is the typical instructions that the agent should give the client.
The authors of the paper hypotheses that the actions are usually around the features of the product. So if they know that a feature is the ``format button'', then they know a verb around that noun will most likely  be an action.

@@

\subsubsection*{Questions and Answers}
Since their input is raw text, the authors mention that in order to capture the questions the use trigger words such as ``how'', ``what'',``where'' which should mark the beginning of a question.\\
Regarding to the answer, it would be the sentence following the question sentence.

@@

The overall construction of the taxonomy given the underlying idea of different granularities of topics seem to work. Nevertheless the reviewer wonders whether the expressiveness and coverage is enough for what it might be real applications that might actually benefit the agents or the users of the callcenter, for example if one were to extend the system into a Question answering System, then this representation will be surely not enough.\\
\\
In ~\cite{DBLP:conf/kdd/LiuSLW12} Liu proposes another method to create a taxonomy from keywords , however they handle different issues which were not addressed by the authors of the reviewed paper, for example fine grain domains and changing domains.\\
Liu proposes using Keywords and not text, since it would provide both an easy way for humans to read the taxonomy and ti will be easier to model how the taxonomy evolves and changes as the domain does.\\
Furthermore, Liu proposes a way to connect the keywords by using text clustering and Information Retrieval, and she addresses many issues not covered by the given paper, this issues are resolved by using information extraction.\\
One of the issues with BoW approach and hierarchical clustering is whether to trust or not the subtyping, for example the concept of ``vehicle insurance'' and ``car insurance''  is clear that the later is a sub type of the earlier. Nevertheless from distributional perspective there is no way for the machine to assure to capture it this way, actually the reviewed paper mentions nothing about this, but it might be possible to have this subtype relations inverted given the distribution of the text. Liu on the other hand proposes to use information extraction snowball approach to look for patterns that might allow to capture some of the subtype, supertype relations, thus leaving this task not only to clustering step.\\
\\
A set of interesting remarks are made by  Bedini and Nguyen in ~\cite{artofontology} in their survey about automatic ontology generation they describe the life cycle of ontology generation. Namely they go in a general description of each phase as:
\begin{itemize}
	\item Extraction: The acquisition of Information and the processing of unstructured and semi-structured data
	\item Analysis: finding the relations and concepts int he given information, using heavily NLP techniques
	\item Generation: Translating the relations and concepts into the ontology formalism, as well as merging ontologies.
	\item Validation: A step to check possible wrong relations, usually as the authors mentioned made manually
	\item Evolution: The possibility of an incrementally growing ontology.
\end{itemize}
For the reviewer this life cycle gives an overview of what the authors of the reviewed paper has done, nevertheless the scalability of the proposed method does not leave space for incremental expansion of the taxonomy, that is in order to give evolution to the proposed methods the authors would have to re-run the whole system with the extra information.

@@

One could clearly see in Table~\ref{table:comparisonTable} that some systems admit some human interventions at some points, this could be beneficial since some steps regarding for example Word Sense Disambiguation could be very sensitive to the over all performance of the system.\\
\\
$Terminae$ ~\cite{BiebowSzulman:99} extracts keywords from the given corpora and hand it to an expert, whose task is to select the relevant terms and conceptualize them. Conceptualizing refers to first give a natural language definition of each term and then expressing it in terms of the chosen formalism to represent the ontology.\\
\\
$Salt$ ~\cite{Lonsdale02pepperingknowledge} on the other hand tries to go further by automatizing more parts of the process. Nevertheless it needs other knowledge sources in order to work. it assumes the existance of 3 types of knowledge: a general Knowledge representation of the domain, a dictionary to discover lexical relations among terms and a consistent set of texts. Salt also allows some interaction with the user, in the last stage for example introduces a new step called ``Constraint Discovery'' in which the user can state things such as ``a person only has one birth date''. \\
\\
The system proposed in Learning an OWL ontology from text ~\cite{citeulike:136652} is more recent than the previous mentioned ones. It heavily relies on Wordnet for connecting concepts. Nevertheless in the paper is mentioned how they extract the keywords that will be used later on in Wordnet, as a remark also nothing is mentioned about the verification process.\\
\\
It is also worth noticing how the reviewed paper does not describe much about the validation process.
Moreover both the extraction and Analysis part seems to be overlapping for the reviewed system, that could be because they proposed a rather simple structure ( Taxonomy of documents) as instead to a more complicated representation such relations among concepts.\\
A more complicated representation would definitely required a clear separation among those two phases, for example the analysis could required syntactic and Semantic processing to solve anaphoras, in order to be able to capture non-obvious relations given in the texts.
